The Globular Cluster System of the Auriga Simulations

### 2019-03-22 AurigaGCS.tex
Bullet point outline of the paragraphs included in the introduction

\section{Introduction}
\todo[inline]{Paragraph: General introduction of GCs}
\begin{itemize}
    \item old, ubiquitous, bright, `simple' single-age stellar populations
    \item properties (particularly metallicity) correlate with the host galaxy
    \item GCs can be used to understand galform, if GCform understood
\end{itemize}
Globular clusters (GCs) are old, ubiquitous, and bright. 
GC ages range from $6-14$~Gyr, although observational age-estimates can be 
uncertain and a definitive age threshold to classify star clusters as `globular' 
remains topic of debate.
GCs are observed at scales ranging from clusters of galaxies down to 
dwarf galaxies 
\todo[inline]{
    \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
}

The properties of the GCs themselves are correlated with those of their host
galaxies, in particular their metallicities. 
\todo[inline]{
    `The mean metallicities of GC systems have long been 
    known to scale with the metallicity of their host (van den Bergh
    1975; Brodie \& Huchra 1991)' \citep[from][]{2008ApJ...681..197P}
}

@@

\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
    previous work and references work of other groups}
% \begin{itemize}
% \item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
% \item GCs in FIRE \citep{2018MNRAS.474.4232K}
% \item EMOSAICS project \citep{2018MNRAS.475.4309P}
% \item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
% \item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
% \item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
% \item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
% \item GC in N-body simulation \citep{2018ApJ...861...69C}
% \item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
% \item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
% \item (GC contribution to EOR \citep{2018MNRAS.479..332B})
% \item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
% \item GC formation in cold filaments \citep{2018ApJ...861..148M}
% \item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
% \item GCs in MW outer region \citep{2017arXiv170804542P}
% \item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
% \item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
% \item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
% \item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
% \item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
% \item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
% \item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
% \item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
% \item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
% \item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
% \item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
% \item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
% \item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
% \item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
% \item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
%     log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
%     $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
%     of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
% \item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
%     of GCs crossing the disk. New kinematical data does not support
%     this claim for two particular OSC-GC pairs, and does seem consistent
%     with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
%     that GC crossing the disk could also trigger formation of multiple OSCs!)
% \item DM halo mass can be inferred from number of globular cluster in galaxy 
%     \citep{2019arXiv190100900B}
% \item GCs in M31 outer halo \citep{2019arXiv190111229W}
% % TODO: last checked arXiv Mar 2, 2019
% \end{itemize}

\todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
    possibly ``Bimodality suggests two formation mechanisms''. In-situ 
    formation vs. accretion in hierarchical build-up of galaxies naturally produces 
    two populations of globular cluster.}
% \begin{itemize}
%     \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
%     \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
%     \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
%     \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media. The red population would form later, once the galactic disc has settled. The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
%     \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
% that major mergers are at the origin of both sub-populations: blue
% clusters form during early mergers (z > 4) while the red ones appear
% in mergers at lower redshifts (even after z = 1). Although, this
% scenario, combined with star formation enhancement in mergers,
% seems appropriate in dense galactic environment leading to the
% assembly of massive elliptical galaxies, like in the Virgo Cluster
% as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
% like systems where no recent major merger took place (Wyse 2001;
% Deason et al. 2013; Ruchti et al. 2014, 2015).
% \item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
% \end{itemize}

\todo[inline]{Paragraph: narrow the scientific motivation down to the scope of 
    this particular work}
\begin{itemize}
    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
    \item Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way (or Andromeda).
    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons. First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters. Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations. The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations. Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations. Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy. This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population. Cosmological zoom simulations uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
\end{itemize}

>>>>

\section{Introduction}
\todo[inline]{Paragraph: General introduction of GCs}
\begin{itemize}
    \item GCs are old, ubiquitous, bright, `simple' single-age stellar populations
    \item GC properties (particularly metallicity) set by birth gas properties, 
        GC properties correlate with their host galaxy properties.
    \item The above makes GCs excellent proxies to study galform
    \item But first GCform should be understood
\end{itemize}
% Globular clusters (GCs) are old, ubiquitous, and bright. 
% GC ages range from $6-14$~Gyr, although observational age-estimates can be 
% uncertain and a definitive age threshold to classify star clusters as `globular' 
% remains topic of debate.
% GCs are observed at scales ranging from clusters of galaxies down to 
% dwarf galaxies 
% \todo[inline]{
%     \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
% }
% 
% The properties of the GCs themselves are correlated with those of their host
% galaxies, in particular their metallicities. 
% \todo[inline]{
%     `The mean metallicities of GC systems have long been 
%     known to scale with the metallicity of their host (van den Bergh
%     1975; Brodie \& Huchra 1991)' \citep[from][]{2008ApJ...681..197P}
% }

\todo[inline]{Paragraph: Theories of GC formation}
\begin{itemize}
    \item Special conditions in early Universe?
    \item Formation in collapsing proto-galaxies (in-situ-ish?)
    \item Formation as a result of (wet) mergers?
    \item Formation in satellites that are later accreted?
    \item No special conditions at high z, but connection between low-z YMC-
        and high-z GC-formation where differences could result from Hubble time
        of evolution?
    \item This means that in order to test formation models against observations,
        one not only needs needs to model GC formation, but also include the full 
        evolution over their lifetime in a cosmological tidal field.
\end{itemize}

\todo[inline]{Paragraph: ingredients for numerical studies}
\begin{itemize}
    \item High resolution in the ISM
    \item Full cosmological evolution
\end{itemize}

@@

% \todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
%     previous work and references work of other groups}
% \begin{itemize}
% \item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
% \item GCs in FIRE \citep{2018MNRAS.474.4232K}
% \item EMOSAICS project \citep{2018MNRAS.475.4309P}
% \item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
% \item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
% \item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
% \item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
% \item GC in N-body simulation \citep{2018ApJ...861...69C}
% \item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
% \item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
% \item (GC contribution to EOR \citep{2018MNRAS.479..332B})
% \item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
% \item GC formation in cold filaments \citep{2018ApJ...861..148M}
% \item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
% \item GCs in MW outer region \citep{2017arXiv170804542P}
% \item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
% \item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
% \item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
% \item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
% \item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
% \item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
% \item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
% \item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
% \item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
% \item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
% \item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
% \item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
% \item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
% \item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
% \item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
%     log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
%     $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
%     of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
% \item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
%     of GCs crossing the disk. New kinematical data does not support
%     this claim for two particular OSC-GC pairs, and does seem consistent
%     with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
%     that GC crossing the disk could also trigger formation of multiple OSCs!)
% \item DM halo mass can be inferred from number of globular cluster in galaxy 
%     \citep{2019arXiv190100900B}
% \item GCs in M31 outer halo \citep{2019arXiv190111229W}
% % TODO: last checked arXiv Mar 2, 2019
% \end{itemize}

% \todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
%     possibly ``Bimodality suggests two formation mechanisms''. In-situ 
%     formation vs. accretion in hierarchical build-up of galaxies naturally produces 
%     two populations of globular cluster.}
% \begin{itemize}
%     \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
%     \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
%     \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
%     \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media. The red population would form later, once the galactic disc has settled. The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
%     \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
% that major mergers are at the origin of both sub-populations: blue
% clusters form during early mergers (z > 4) while the red ones appear
% in mergers at lower redshifts (even after z = 1). Although, this
% scenario, combined with star formation enhancement in mergers,
% seems appropriate in dense galactic environment leading to the
% assembly of massive elliptical galaxies, like in the Virgo Cluster
% as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
% like systems where no recent major merger took place (Wyse 2001;
% Deason et al. 2013; Ruchti et al. 2014, 2015).
% \item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
% \end{itemize}

\todo[inline]{Paragraph: narrow down to this work}
\begin{itemize}
    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
    \item Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way (or Andromeda).
    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons. First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters. Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations. The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations. Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations. Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy. This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population. Cosmological zoom simulations uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
\end{itemize}
